Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix typo: s/uses/used/
Shorten sentence, subtly broaden meaning.
My first thought on reading this sentence was: "But you could *write* in
ClojureScript, or anything else that targets JS..." And then I realized this
proposed change could save you some words and avoid any implication that one
must author JavaScript to use the WebRTC browser APIs.

To establish a direct communication channel between browsers, WebRTC
uses a mechanism called Interactive Connectivity Establishment (ICE)
that is similar to the Session Initiation Protocol (SIP) commonly used
for Voice-over-IP (VoIP) communication \cite{RFC5245:ice}. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also uses to communicate session control messages
(open, close, error) and to negotiate media capabilities. %TODO/CITE
The signaling server may optionally provide other services such as
higher level session management, HTTP serving of the web application,
address book service, client presence/availability, etc. %TODO/CITE

@@

The WebRTC browser APIs enable web applications written in JavaScript
to establish browser-to-browser network connectivity in order to
perform real-time video, audio and data communication. These APIs are
currently in the process of being standardized by the \emph{Web
Real-Time Communications Working Group} of the World Wide Web
Consortium (W3C) \cite{webrtc:wg}.

>>>>

To establish a direct communication channel between browsers, WebRTC
uses a mechanism called Interactive Connectivity Establishment (ICE)
that is similar to the Session Initiation Protocol (SIP) commonly used
for Voice-over-IP (VoIP) communication \cite{RFC5245:ice}. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also used to communicate session control messages
(open, close, error) and to negotiate media capabilities. %TODO/CITE
The signaling server may optionally provide other services such as
higher level session management, HTTP serving of the web application,
address book service, client presence/availability, etc. %TODO/CITE

@@

The WebRTC browser APIs enable JavaScript web applications
to establish browser-to-browser network connectivity in order to
perform real-time video, audio and data communication. These APIs are
currently in the process of being standardized by the \emph{Web
Real-Time Communications Working Group} of the World Wide Web
Consortium (W3C) \cite{webrtc:wg}.
